Supplementary material for referee\\MNRAS: MN-15-0213-MJ

### 2015-03-26 draft.tex
a few more slight changes

In our implementation of the macro-atom approach, we also explicitly
take into account the photoionization and collisional ionization rates
between a lower level, $l$, and the continuum (or, in the case of ions
with more than one bound electron, the ground state of the upper ion),
$\kappa$,
\begin{equation}
{\cal R}_{l \kappa}= n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu}
  \sigma_{\nu}}{h \nu} d\nu + C_{l \kappa} n_l n_e.
\end{equation}
Here, $\sigma_{\nu}$ is the photoionization cross section, and $J_{\nu}$
is the mean intensity. The corresponding recombination rate is given
by 
\begin{equation}
{\cal R}_{\kappa l} = \alpha_{\kappa l} n_{\kappa} n_e + C_{\kappa l}
n_\kappa n_e, \\
\end{equation}
where $\alpha_{\kappa l}$ is the radiative recombination coefficient
to level $l$. This treatment means that radiative and collisional
rates to and from all levels are considered when calculating both the
ionization state and the level populations, although we neglect 
ionization directly to excited levels of the upper ion. The
\cite{vanregemorter} approximation is used for collisional
transitions. This means that collisions between radiatively
forbidden transitions are not taken into account when one 
splits levels according to $l$- and $s$-subshells, as well
as principal quantum number, $n$ (as we have done with He~\textsc{i}; 
see section~\ref{sec:data}). Although this is, in general, 
a poor approximation, it is a second order effect in the physical 
regime where recombination lines are formed. This is because bound-free processes are 
dominant in determining level populations and emissivities.
We have verified that this is indeed the case in the He~\textsc{i}
emission regions in our model.

>>>>

In our implementation of the macro-atom approach, we also explicitly
take into account the photoionization and collisional ionization rates
between a lower level, $l$, and the continuum (or, in the case of ions
with more than one bound electron, the ground state of the upper ion),
$\kappa$,
\begin{equation}
{\cal R}_{l \kappa}= n_l \int_{\nu_0}^{\infty} \frac{ 4 \pi J_{\nu}
  \sigma_{\nu}}{h \nu} d\nu + C_{l \kappa} n_l n_e.
\end{equation}
Here, $\sigma_{\nu}$ is the photoionization cross section, and $J_{\nu}$
is the mean intensity. The corresponding recombination rate is given
by 
\begin{equation}
{\cal R}_{\kappa l} = \alpha_{\kappa l} n_{\kappa} n_e + C_{\kappa l}
n_\kappa n_e, \\
\end{equation}
where $\alpha_{\kappa l}$ is the radiative recombination coefficient
to level $l$. This treatment means that radiative and collisional
rates to and from all levels are considered when calculating both the
ionization state and the level populations, although we neglect 
ionization directly to excited levels of the upper ion. The
\cite{vanregemorter} approximation is used for collisional
transitions. This means that collisions between radiatively
forbidden transitions are not taken into account when one 
splits levels ito $l$- and $s$-subshells, as well
as principal quantum number, $n$ (as we have done with He~\textsc{i}; 
see section~\ref{sec:data}). Although this approximation is, in general, 
a poor one, the effect is second order in the physical 
regime where recombination lines are formed in our models. 
This is because bound-free processes are dominant in determining 
level populations and emissivities. We have verified that this 
is indeed the case in the He~\textsc{i} emission regions in our models.

### 2015-03-26 response/supplement_response.tex
a few more slight changes

\begin{figure}	%fullpage
\centering
\includegraphics[width=1.0\textwidth]{pops.png}
\caption{
}
\label{novalikes}
\end{figure}

>>>>

This is a supplementary documenting which presents a few plots to justify the claims made in the response to
referee for MNRAS submission MN-15-0213-MJ.

Figure 1 shows the level populations of Helium 1. Levels are split according to TopBase, meaning that they are in 
energy order and split by s and l quantum numbers.It demonstrates that in the dense regions of the wind in which He I emission tends to occur (Cell 10), the populations are already more or less distributed by statistical weight. The cells in the figure have the following properties:

\begin{itemize}
\item cell 10: $T_R=4.76e+04, T_e=3.43e+04, n_e=1.10e+14, W=3.49e-01$
\item cell 96: $T_R=4.69e+04, T_e=1.96e+04, n_e=5.26e+10, W=6.02e-03$
\item cell 200: $T_R=3.41e+04, T_e=1.49e+03, n_e=5.87e+07, W=1.41e-04$
\end{itemize}
Figure 2 shows a spectrum. One of the models has arbritrarily fast transitions added between forbidden transitions,
to simulate the effect of dominant collisional transitions between these states. The other model is model B from the 
paper, a model with significant He I emission. The effect on the overall spectrum is completely negligible.

\begin{figure}	%fullpage
\centering
\includegraphics[width=1.0\textwidth]{pops.png}
\caption
{
Top Panel: fractional level populations in He I. Bottom Panel: fractional level populations in He I divided by statistical weight. In dense regions the levels are already distributed more or less according to statistical weight. This
is due to b-f processes dominating the level populations. As densities decrease, the triplet and singlet populations
become somewhat decoupled. This does not affect the model as these cells have negligible line emissivities.
}
\label{f1}
\end{figure}

\begin{figure}	%fullpage
\centering
\caption{
A spectrum will be shown here.
}
\label{f2}
\end{figure}
